Final JCGS Cover Letter

### 2022-10-11 Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
made final revisions.

\bigskip
\begin{abstract}
How do statistical regression results compare to intuitive, visually
fitted results? Fitting lines by eye through a set of points has been
explored since the 20th century. Common methods of fitting trends by eye
involve maneuvering a string, black thread, or ruler until the fit is
suitable, then drawing the line through the set of points. In 2015, the
New York Times introduced an interactive feature, called `You Draw It',
where readers were asked to input their own assumptions about various
metrics and compare how these assumptions relate to reality. In this
paper, we validate `You Draw It' as a method for graphical testing,
comparing results to the less technological method utilized in
\citet{mosteller1981eye} and extending that study with formal
statistical analysis methods. Results were consistent with those found
in the previous study; when shown points following a linear trend,
participants tended to fit the slope of the first principal component
over the slope of the least-squares regression line. This trend was most
prominent when shown data simulated with larger variances. This study
reinforces the differences between intuitive visual model fitting and
statistical model fitting, providing information about human perception
as it relates to the use of statistical graphics.
\end{abstract}

@@

We need human testing of graphics in order to draw broad conclusions,
develop guidelines for graphical design, and improve graphical
communication. Studies might ask participants to identify differences in
graphs, read information off of a chart accurately, use data to make
correct real-world decisions, or predict the next few observations. All
of these types of tests require different levels of use and manipulation
of the information being presented in the chart. Early research studies
considered graphs from a psychological perspective
\citep{spence1990visual, lewandowsky1989perception}, testing
participants' abilities to detect a stimulus or a difference between two
stimuli. Psychophysical methods have been used to test graphical
perception, as in \citet{vanderplas2015signs}, which used the method of
adjustment - a technique which requires participants to alter a changing
stimulus to match a given constant stimuli \citep{gescheider_1997}- to
estimate the magnitude of the impact of the sine illusion. However,
there are more modern testing methods that have been developed since the
heyday of psychophysics.

One major development in statistical graphics which led to more advanced
testing methods is Wilkinson's Grammar of Graphics
\citep{wilkinson2013grammar}. The Grammar of Graphics serves as the
fundamental framework for data visualization with the notion that
graphics are built from the ground up by specifying exactly how to
create a particular graph from a given data set. Visual representations
are constructed through the use of ``tidy data'' which is characterized
as a data set in which each variable is in its own column, each
observation is in its own row, and each value is in its own cell
\citep{wickham2016r}. Graphics are viewed as a mapping from variables in
a data set (or statistics computed from the data) to visual attributes
such as the axes, colors, shapes, or facets on the canvas in which the
chart is displayed. Software, such as Hadley Wickham's ggplot2
\citep{wickham2011ggplot2}, aims to implement the framework of creating
charts and graphics as the Grammar of Graphics recommends.

@@

In \citet{ciccione2021can}, participants were asked to judge trends,
estimate slopes, and conduct extrapolation. To estimate slopes,
participants were asked to report the slope of the best-fitting
regression line using a track-pad to adjust the tilt of a line on the
screen. Results indicated the slopes participants reported were always
in excess of the ideal slopes, both in the positive and in the negative
direction, and those biases increase with noise and with number of
points. This supports the results found in \citet{mosteller1981eye} and
suggest that participants might use Deming regression
\citep{deming1943statistical, linnet1998performance, martin2000general},
which minimizes the Euclidean distance of points from the line, when
fitting a line to a noisy scatterplot.

@@

Participants were recruited through through Twitter, Reddit, and direct
email in May 2021. A total of 35 individuals completed 131 unique `You
Draw It' task plots. Data were collected as a part of a pilot study
meant to test the applet; therefore, either voluntary participant
dropout or disconnection from a server not designed to accommodate large
magnitudes of participants resulted in missing plots in our data set for
analysis. All participants had normal or corrected to normal vision and
signed an informed consent form. The experimental tasks took
approximately 15 minutes to complete. As this is a pilot study,
participants from Twitter and Reddit pages related to data visualization
voluntarily completed the study and likely had an interest in fields
related to statistics and wanted to help advance research in graphics.
While this study does utilize a convenience sample, as this is primarily
a perceptual task, previous results have found few differences between
expert and non-expert participants in this context
\citep{vanderplas2015spatial}. These data were collected to validate
this method of graphical testing, with the hopes of providing a new tool
to assess graphical perception interactively. Participants completed the
experiment on their own computers in an environment of their choosing.
The experiment was conducted and distributed through a Shiny application
\citep{shinyPkg} found at
\url{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}.

@@

In the study, participants were shown an interactive scatterplot
(\cref{fig:ydi-stimuli}) along with the prompt, ``Use your mouse to fill
in the trend in the yellow box region.'' The yellow box region moved
along as the user drew their trend-line, providing a visual cue which
indicates where the user still needed to complete a trend line. After
the entire domain had been visually estimated or predicted, the yellow
shaded region disappeared, indicating the participant had completed the
task. Data Driven Documents (D3), a JavaScript-based graphing framework
that facilitates user interaction, was used to create the `You Draw It'
visual. In order to allow for user interaction and data collection, we
integrated the D3 visual into Shiny using the \texttt{r2d3} R package
\citep{r2d3}. While the interface is highly customized to this
particular task, we hope to generalize the code and provide a Shiny
widget in an R package soon.

@@

All data processing was conducted in R software environment for
statistical computing and graphics \citep{Rsoftware}. A total of
\(N = 30\) points \((x_i, y_i), i = 1,...,N\) were generated for
\(x_i \in [x_{min}, x_{max}]\) where \(x\) and \(y\) have a linear
relationship. Data were simulated based on the point-slope form of a
linear model with additive errors: \begin{align}
y_i = \beta_1(x_i-\bar{x}) + y_{\bar{x}} + e_i \\
\text{with } e_i & \sim N(0, \sigma^2). \nonumber
\end{align}

where \(\beta_1\) represents the slope of the trend and \(y_{\bar{x}}\)
represents the \(y\) value at the mean of the generated \(x\) values.
Model equation parameters, \(\beta_1\), \(y_{\bar{x}}\), and parameter
choice letter names (S, F, V, N), were selected to reflect the four data
sets used and labeled in \citet{mosteller1981eye}
(\cref{tab:eyefitting-parameters}). The point \((x, y_{\bar{x})}\) was
used in the point-slope equation of a line. Parameter choices S, F, and
N simulated data across a domain of 0 to 20. Parameter choice F produced
a trend with a positive slope and a large variance while N had a
negative slope and a large variance. In comparison, S showed a trend
with a positive slope and a small variance while V yielded a steep
positive slope with a small variance over the domain of 4 to 16.
\cref{fig:eyefitting-simplot} illustrates an example of simulated data
for all four parameter choices intended to reflect the trends in
\citet{mosteller1981eye}. Aesthetic design choices were made consistent
across each of the interactive `You Draw It' task plots. The y-axis
range extended 10\% beyond (above and below) the range of the simulated
data points to allow for users to draw outside the simulated data set
range and avoid anchoring their lines to the corners of the plot.

@@

Due to the randomness in the data generation process, the actual slope
of the linear regression line fit through the simulated points could
differ from the predetermined slope. Therefore, we fit an OLS regression
to each scatterplot to obtain estimated parameters \(\hat\beta_{0,OLS}\)
and \(\hat\beta_{1,OLS}\). Fitted values, \(\hat y_{k,OLS}\), were then
obtained every 0.25 increment across the domain from the OLS regression
equation,
\(\hat y_{k,OLS} = \hat\beta_{0,OLS} + \hat\beta_{1,OLS} x_k\), for
\(k = 1, ..., 4 x_{max} +1\). The PA regression slope,
\(\hat\beta_{1,PA}\), and y-intercept, \(\hat\beta_{0,PA}\), were
determined using the \texttt{mcreg} function in the mcr package in R
\citep{mcr_pkg} which implements Deming regression (equivalent to a
regression based on the slope of the first principal axis). Fitted
values, \(\hat y_{k,PA}\) were then obtained every 0.25 increment across
the domain from the PA regression equation,
\(\hat y_{k,PA} = \hat\beta_{0,PA} + \hat\beta_{1,PA} x_k\), for
\(k = 1, ..., 4 x_{max} +1\).

@@

The intent of this research was to adapt `You Draw It' from the New York
Times feature as a tool and method for testing graphics and introduce a
method for statistically modeling the participant drawn lines. We
provided support for the validity of the `You Draw It' method by
replicating the study found in \citet{mosteller1981eye}. Using
generalized additive mixed models, we assessed the deviation of the
participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend,
participants visually fit a regression line that mimics the first
principal axis regression as opposed to ordinary least squares
regression. Data simulated with a larger variance provided strong
support for a participants tendency to visually fit the first principal
axis regression. We utilized modern technology to replicate a study
conducted 40 years ago, and strengthened the original results with
current analysis methods which allow for more flexibility and
sophistication. Our results indicate that participants minimized the
distance from their drawn regression line over both the \(x\) and \(y\)
axis simultaneously. We allowed participants to draw trend lines that
deviated from a straight line and gained an insight into the curvature
the human eye perceives in a set of points. Researchers in cognitive and
human movement sciences have found that human arm movement is a complex
task \citep{miall1995curvature, rousset2015study}. The `You Draw It'
method described in this paper uses \emph{indirect interaction} in which
the mouse position and resulting visual line on the screen are
dissociated. Therefore, curvature found in participant drawn lines from
a straight lines could potentially be explained by the lack of
coordination which results from the eye-hand dissociation from indirect
drawing and the distortion of visual perception affecting the curvature
of movements. Additionally, there is a training effect related to the
completion of the `You Draw It' task - the movement of the line must be
slow so that the visual representation on the screen can accurately
capture each movement. \citet{de1991misdirections} conducted a study in
which participants moved their hand slowly from an initial position in
front of them to a visual target (movement task); they were then asked
to repeat the task using different sizes of pointers (perceptual task).
Their results indicated that deviations from the shortest pointers were
comparable to those of the movement task, but that bias increased as the
length of the pointer increased. While we suggested participants use a
mouse to complete the study, we could not require the use; therefore,
some participants may have used a track-pad and results may have been
influenced by the pressure placed on their track-pad
\citep{easton1978finger}. In cognitive psychology, \citet{cui_2018}
studied the improvement in estimating correlations in scatter plots
through perceptual learning interventions.\\
Their study provided support for an improved proficiency in correlation
estimation after training. We used a randomized complete design
experimental structure, while \citet{mosteller1981eye} implemented a
latin square design to test for an order effect due to practice.

@@

This study provided a basis for the use of `You Draw It' as a tool for
testing statistical graphics and introduced a method for statistically
modeling participant drawn lines using generalized additive mixed
models. Additional studies related to the validation and use of the tool
would be useful for providing insight into explanations of biases
introduced by the task such as the deviation from a straight line. For
instance, a variation on the current study could compare manual
adjustment methods such as shifting and rotating a horizontal line
segment until the fit is suitable to the `You Draw It' method on the
same set of data. This might explain the large deviation from the
participant drawn line as \(x\) approaches 20. Another useful extension
study would be to compare the `You Draw It' method as conducted by
direct interaction - using a digital pen on a tablet - to indirect
interaction - using a computer mouse to relate to a pointer on the
screen. Previous studies investigated human ability to perform
regressions over scatterplots with outliers and found participant
estimated trend lines to be closer to a robust trend line than the
statistically fitted trend line where outliers were included
\citep{bobko_1979, correll_2017}. This work could provide an extension
and further evaluate the perceptual system's resistance to outliers by
allowing participants to deviate from a straight line, potentially
capturing the outlier(s). While the focus of this study was on drawing
linear trend-lines, further investigation is necessary to implement this
method in non-linear settings and with real data in order to facilitate
scientific communication - a strength of the combination of the flexible
`You Draw It' method and GAMM analysis method. \citet{ciccione2021can}
evaluated human ability to extrapolate data from trends by asking
participants to provide a single point estimate; this tool could be used
to evaluate a continuous extrapolation of points from a trend line for
various linear and non-linear data structures. In the future, we intend
to create an R package designed for easy implementation of `You Draw It'
task plots in order to make this tool accessible to other researchers.

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses (eyefitting-model-data.csv).
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper (you-draw-it-eyefitting-analysis.Rmd).
\item
  \textbf{README:} File containing detailed descriptions of the
  supplementary material (README.html).
\end{itemize}

>>>>

\bigskip
\begin{abstract}
How do statistical regression results compare to intuitive, visually
fitted results? Fitting lines by eye through a set of points has been
explored since the 20th century. Common methods of fitting trends by eye
involve maneuvering a string, black thread, or ruler until the fit is
suitable, then drawing the line through the set of points. In 2015, the
New York Times introduced an interactive feature, called `You Draw It',
where readers were asked to input their own assumptions about various
metrics and compare how these assumptions relate to reality. In this
paper, we validate `You Draw It' as a method for graphical testing,
comparing results to the less technological method utilized in
\citet{mosteller1981eye} and extending that study with formal
statistical analysis methods. Results were consistent with those found
in the previous study; when shown points following a linear trend,
participants tended to fit the slope of the principal axis over the
slope of the least-squares regression line. This trend was most
prominent when shown data simulated with larger variances. This study
reinforces the differences between intuitive visual model fitting and
statistical model fitting, providing information about human perception
as it relates to the use of statistical graphics.
\end{abstract}

@@

We need human testing of graphics in order to draw broad conclusions,
develop guidelines for graphical design, and improve graphical
communication. Studies might ask participants to identify differences in
graphs, read information off of a chart accurately, use data to make
correct real-world decisions, or predict the next few observations. All
of these types of tests require different levels of use and manipulation
of the information being presented in the chart. Early research studies
considered graphs from a psychological perspective
\citep{spence1990visual, lewandowsky1989perception}, testing
participants' abilities to detect a stimulus or a difference between two
stimuli. Psychophysical methods have been used to test graphical
perception, as in \citet{vanderplas2015signs}, which used the method of
adjustment - a technique which requires participants to alter a changing
stimulus to match a given constant stimuli \citep{gescheider_1997} - to
estimate the magnitude of the impact of the sine illusion. However,
there are more modern testing methods that have been developed since the
heyday of psychophysics.

One major development in statistical graphics which led to more advanced
testing methods is Wilkinson's Grammar of Graphics
\citep{wilkinson2013grammar}. The Grammar of Graphics serves as the
fundamental framework for data visualization with the notion that
graphics are built from the ground up by specifying exactly how to
create a particular graph from a given data set. Visual representations
are constructed through the use of ``tidy data'' which is characterized
as a data set in which each variable is in its own column, each
observation is in its own row, and each value is in its own cell
\citep{wickham2016r}. Graphics are viewed as a mapping from variables in
a data set (or statistics computed from the data) to visual attributes
such as the axes, colors, shapes, or facets on the canvas in which the
chart is displayed. Software, such as Hadley Wickham's \texttt{ggplot2}
package in R \citep{wickham2011ggplot2}, aims to implement the framework
of creating charts and graphics as the Grammar of Graphics recommends.

@@

In \citet{ciccione2021can}, participants were asked to judge trends,
estimate slopes, and conduct extrapolation. To estimate slopes,
participants were asked to report the slope of the best-fitting
regression line using a track-pad to adjust the tilt of a line on the
screen. Results indicated the slopes participants reported were always
in excess of the ideal slopes, both in the positive and in the negative
direction, and those biases increase with noise and with number of
points. This supports the results found in \citet{mosteller1981eye} and
suggest that participants might use Deming regression
\citep{deming1943statistical, linnet1998performance, martin2000general},
which is equivalent to the principal axis and minimizes the Euclidean
distance of points from the line, when fitting a line to a noisy
scatterplot.

@@

Participants were recruited through Twitter, Reddit, and direct email in
May 2021. A total of 35 individuals completed 131 unique `You Draw It'
task plots. Data were collected as a part of a pilot study meant to test
the applet; therefore, either voluntary participant dropout or
disconnection from a server not designed to accommodate large magnitudes
of participants resulted in missing plots in our data set for analysis.
All participants had normal or corrected to normal vision and signed an
informed consent form. The experimental tasks took approximately 15
minutes to complete. As this is a pilot study, participants from Twitter
and Reddit pages related to data visualization voluntarily completed the
study and likely had an interest in fields related to statistics and
wanted to help advance research in graphics. While this study does
utilize a convenience sample, as this is primarily a perceptual task,
previous results have found few differences between expert and
non-expert participants in this context \citep{vanderplas2015spatial}.
These data were collected to validate this method of graphical testing,
with the hopes of providing a new tool to assess graphical perception
interactively. Participants completed the experiment on their own
computers in an environment of their choosing. The experiment was
conducted and distributed through a R Shiny application \citep{shinyPkg}
found at
\url{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}.

@@

In the study, participants were shown an interactive scatterplot
(\cref{fig:ydi-stimuli}) along with the prompt, ``Use your mouse to fill
in the trend in the yellow box region.'' The yellow box region moved
along as the user drew their trend-line, providing a visual cue which
indicates where the user still needed to complete a trend line. After
the entire domain had been visually estimated or predicted, the yellow
shaded region disappeared, indicating the participant had completed the
task. Data Driven Documents (D3), a JavaScript-based graphing framework
that facilitates user interaction, was used to create the `You Draw It'
visual. In order to allow for user interaction and data collection, we
integrated the D3 visual into R Shiny using the \texttt{r2d3} R package
\citep{r2d3}. While the interface is highly customized to this
particular task, we hope to generalize the code and provide a Shiny
widget in an R package soon.

@@

All data processing was conducted in R software environment for
statistical computing and graphics \citep{Rsoftware}. A total of
\(N = 30\) points \((x_i, y_i), i = 1,...,N\) were generated for
\(x_i \in [x_{min}, x_{max}]\) where \(x\) and \(y\) have a linear
relationship. Data were simulated based on the point-slope form of a
linear model with additive errors: \begin{align}
y_i = \beta_1(x_i-\bar{x}) + y_{\bar{x}} + e_i \\
\text{with } e_i & \sim N(0, \sigma^2). \nonumber
\end{align} where \(\beta_1\) represents the slope of the trend and
\(y_{\bar{x}}\) represents the \(y\) value at the mean of the generated
\(x\) values. Model equation parameters, \(\beta_1\), \(y_{\bar{x}}\),
and parameter choice letter names (S, F, V, N), were selected to reflect
the four data sets used and labeled in \citet{mosteller1981eye}
(\cref{tab:eyefitting-parameters}). The point \((x, y_{\bar{x})}\) was
used in the point-slope equation of a line. Parameter choices S, F, and
N simulated data across a domain of 0 to 20. Parameter choice F produced
a trend with a positive slope and a large variance while N had a
negative slope and a large variance. In comparison, S showed a trend
with a positive slope and a small variance while V yielded a steep
positive slope with a small variance over the domain of 4 to 16.
\cref{fig:eyefitting-simplot} illustrates an example of simulated data
for all four parameter choices intended to reflect the trends in
\citet{mosteller1981eye}. Aesthetic design choices were made consistent
across each of the interactive `You Draw It' task plots. The \(y\)-axis
range extended 10\% beyond (above and below) the range of the simulated
data points to allow for users to draw outside the simulated data set
range and avoid anchoring their lines to the corners of the plot.

@@

Due to the randomness in the data generation process, the actual slope
of the linear regression line fit through the simulated points could
differ from the predetermined slope. Therefore, we fit an OLS regression
to each scatterplot to obtain estimated parameters \(\hat\beta_{0,OLS}\)
and \(\hat\beta_{1,OLS}\). Fitted values, \(\hat y_{k,OLS}\), were then
obtained every 0.25 increment across the domain from the OLS regression
equation,
\(\hat y_{k,OLS} = \hat\beta_{0,OLS} + \hat\beta_{1,OLS} x_k\), for
\(k = 1, ..., 4 x_{max} +1\). The PA regression slope,
\(\hat\beta_{1,PA}\), and \(y\)-intercept, \(\hat\beta_{0,PA}\), were
determined using the \texttt{mcreg} function in the mcr package in R
\citep{mcr_pkg} which implements Deming regression (equivalent to a
regression based on the slope of the principal axis). Fitted values,
\(\hat y_{k,PA}\) were then obtained every 0.25 increment across the
domain from the PA regression equation,
\(\hat y_{k,PA} = \hat\beta_{0,PA} + \hat\beta_{1,PA} x_k\), for
\(k = 1, ..., 4 x_{max} +1\).

@@

The intent of this research was to adapt `You Draw It' from the New York
Times feature as a tool and method for testing graphics and introduce a
method for statistically modeling the participant drawn lines. We
provided support for the validity of the `You Draw It' method by
replicating the study found in \citet{mosteller1981eye}. Using
generalized additive mixed models, we assessed the deviation of the
participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend,
participants visually fit a regression line that mimics the principal
axis regression line as opposed to ordinary least squares regression
line. Data simulated with a larger variance provided strong support for
a participants tendency to visually fit the first principal axis
regression. We utilized modern technology to replicate a study conducted
40 years ago, and strengthened the original results with current
analysis methods which allow for more flexibility and sophistication.
Our results indicate that participants minimized the distance from their
drawn regression line over both the \(x\) and \(y\) axis simultaneously.
We allowed participants to draw trend lines that deviated from a
straight line and gained an insight into the curvature the human eye
perceives in a set of points.

Researchers in cognitive and human movement sciences have found that
human arm movement is a complex task
\citep{miall1995curvature, rousset2015study}. The `You Draw It' method
described in this paper uses \emph{indirect interaction} in which the
mouse position and resulting visual line on the screen are dissociated.
Therefore, curvature found in participant drawn lines from a straight
lines could potentially be explained by the lack of coordination which
results from the eye-hand dissociation from indirect drawing and the
distortion of visual perception affecting the curvature of movements.
Additionally, there is a training effect related to the completion of
the `You Draw It' task - the movement of the line must be slow so that
the visual representation on the screen can accurately capture each
movement. \citet{de1991misdirections} conducted a study in which
participants moved their hand slowly from an initial position in front
of them to a visual target (movement task); they were then asked to
repeat the task using different sizes of pointers (perceptual task).
Their results indicated that deviations from the shortest pointers were
comparable to those of the movement task, but that bias increased as the
length of the pointer increased. While we suggested participants use a
mouse to complete the study, we could not require the use; therefore,
some participants may have used a track-pad and results may have been
influenced by the pressure placed on their track-pad
\citep{easton1978finger}. In cognitive psychology, \citet{cui_2018}
studied the improvement in estimating correlations in scatter plots
through perceptual learning interventions. Results form their study
provided support for an improved proficiency in correlation estimation
after training. We used a randomized complete design experimental
structure, while \citet{mosteller1981eye} implemented a latin square
design to test for an order effect due to practice.

@@

This study provided a basis for the use of `You Draw It' as a tool for
testing statistical graphics and introduced a method for statistically
modeling participant drawn lines using generalized additive mixed
models. Additional studies related to the validation and use of the tool
would be useful for providing insight into explanations of biases
introduced by the task such as the deviation from a straight line. For
instance, a variation on the current study could compare manual
adjustment methods such as shifting and rotating a horizontal line
segment until the fit is suitable to the `You Draw It' method on the
same set of data. This might explain the large deviation from the
participant drawn line as \(x\) approaches 20. Another useful extension
study would be to compare the `You Draw It' method as conducted by
direct interaction - using a digital pen on a tablet - to indirect
interaction - using a computer mouse to relate to a pointer on the
screen. Previous studies investigated human ability to perform
regressions over scatterplots with outliers and found participant
estimated trend lines to be closer to a robust trend line than the
statistically fitted trend line where outliers were included
\citep{bobko_1979, correll_2017}. The work in this paper could provide
an extension and further evaluate the perceptual system's resistance to
outliers by allowing participants to deviate from a straight line,
potentially capturing the outlier(s). While the focus of this study was
on drawing linear trend lines, further investigation is necessary to
implement this method in nonlinear settings and with real data in order
to facilitate scientific communication - a strength of the combination
of the flexible `You Draw It' method and GAMM analysis method.
\citet{ciccione2021can} evaluated human ability to extrapolate data from
trends by asking participants to provide a single point estimate; this
tool could be used to evaluate a continuous extrapolation of points from
a trend line for various linear and nonlinear data structures. In the
future, we intend to create an R package designed for easy
implementation of `You Draw It' task plots in order to make this tool
accessible to other researchers.

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses (eyefitting-model-data.csv).
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper (you-draw-it-eyefitting-analysis.Rmd).
\item
  \textbf{readme:} File containing detailed descriptions of the
  supplementary material (README.html).
\end{itemize}

### 2022-10-11 manuscript-revisions/final-submission-cover-letter.qmd
made final revisions.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.pdf`
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd`
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex`
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.pdf`
+ `bibliography.bib`
+ `agsm.bst`
+ `images/ydi-stimuli.png`
+ `figure-latex/eyefitting-example-plot-1.pdf`
+ `figure-latex/eyefitting-gamm-residualplots-1.pdf`
+ `figure-latex/eyefitting-lmer-residualplots-1.pdf`
+ `figure-latex/eyefitting-simplot-1.pdf`
+ `figure-latex/ols-vs-pca-example-1.pdf`

@@

+ `README.html` 
+ `eyefitting-model-data.csv`
+ `you-draw-it-eyefitting-analysis.Rmd`

>>>>

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.pdf` Final pdf version of manuscript.
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd` Final rmarkdown document used to write the manuscript with the proper formatting.
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex` Final latex file outputted from the rmarkdown document.
+ `bibliography.bib` File containing references in bibtex format.
+ `agsm.bst`
+ `images/ydi-stimuli.png` Image for Figure 1 in the manuscript.
+ `figure-latex/eyefitting-simplot-1.pdf` Image for Figure 2 in the manuscript; originally created using R ggplot2 code within the rmarkdown file.
+ `figure-latex/ols-vs-pca-example-1.pdf` Image for Figure 3 in the manuscript; originally created using R ggplot2 code within the rmarkdown file.
+ `figure-latex/eyefitting-example-plot-1.pdf` Image for Figure 4 in the manuscript; originally created using R ggplot2 code within the rmarkdown file.
+ `figure-latex/eyefitting-lmer-residualplots-1.pdf` Image for Figure 5 in the manuscript; originally created using R ggplot2 code within the rmarkdown file. This image is to be printed in color.
+ `figure-latex/eyefitting-gamm-residualplots-1.pdf` Image for Figure 6 in the manuscript; originally created using R ggplot2 code within the rmarkdown file. This image is to be printed in color.

@@

+ `README.html` File containing detailed descriptions of the supplementary material.
+ `eyefitting-model-data.csv` De-identified participant data collected in the study and used for analyses.
+ `you-draw-it-eyefitting-analysis.Rmd` The .Rmd code file used to replicate the analysis in this paper.
